Project Phase 1
Alex Lang
```{r}
install.packages('gridExtra')
install.packages('ggcorrplot')
```

```{r}
library(tidyverse)
library(tidymodels)
library(GGally)
library(ggcorrplot)
library(gridExtra)
```

Reading in and Renaming Dataset
```{r}
house = ames_student_1
```
```{r}
str(house)
summary(house)
```
Mutating variables
```{r}
house = house %>% mutate(Above_Median = as_factor(Above_Median)) %>% 
  mutate(Above_Median = fct_recode(Above_Median, "No" = "0", "Yes" = "1" )) %>% 
  mutate(Overall_Qual= as_factor(Overall_Qual))
summary(house)
```
Looking at house built after median year built, 1972
```{r}
houseyear1 = house %>% filter(Year_Built>1972)
houseyear2 = house %>% filter(Year_Built<=1972)
summary(houseyear1)
summary(houseyear2)
```
Creating a scatter plot to show which houses were above median based off Year Built
```{r}
p1 = ggplot(house, aes(x=Year_Built,y=Above_Median)) + geom_point()+theme_bw()
grid.arrange(p1)
```
Creating a bar plot that shows count of above_median homes by neighborhood
```{r}
p2 = ggplot(house) +geom_bar(aes(x = Neighborhood)) +ylab("Above_Median")
grid.arrange(p2)
```
Creating a bar plot that shows count of homes by Overall_Qual
```{r}
ggplot(house, aes(x=Overall_Qual)) +geom_bar()
```
Creating a new variable that sums 1st floor sqft plus 2nd floor sqft to find mean sqft. 
```{r}
housesqft = house$First_Flr_SF + house$Second_Flr_SF
summary(housesqft)
```
Using mean sqft to fund houses below and above average
```{r}
house = data.frame(house,housesqft)
```
```{r}
housesqft1 = house %>% filter(housesqft>1494)
housesqft2 = house %>% filter(housesqft<=1494)
summary(housesqft1)
summary(housesqft2)
```

